Barneby Lives!

### 2023-06-18 scripts/Barneby_Lives.Rmd
resolved merge via load library

```{r Libraries, message=FALSE, warning=FALSE}
#install.packages("WorldFlora", "elevatr")
library(tidyverse)
library(sf)
#library(parzer)
library(tigris)
#library(WorldFlora)
library(elevatr)
library(googlesheets4)
```

>>>>

```{r Libraries, message=FALSE, warning=FALSE}
#install.packages("WorldFlora", "elevatr")
library(tidyverse)
library(sf)
#library(parzer)
#library(WorldFlora)
library(elevatr)
library(googlesheets4)
```

### 2023-06-18 scripts/taxonomy_setup.Rmd
resolved merge via load library

write.csv(sppLKPtab, '../taxonomic_data/species_lookup_table.csv', row.names = F)
write.csv(epiLKPtab, '../taxonomic_data/epithet_lookup_table.csv', row.names = F)
write.csv(genLKPtab, '../taxonomic_data/genus_lookup_table.csv', row.names = F)

```

>>>>

write.csv(sppLKPtab, '../taxonomic_data/species_lookup_table.csv', row.names = F)
write.csv(epiLKPtab, '../taxonomic_data/epithet_lookup_table.csv', row.names = F)
write.csv(genLKPtab, '../taxonomic_data/genus_lookup_table.csv', row.names = F)
```
